\chapter{People}
\label{chap:auth}

The {\lpmd} code had been developed by \textbf{Joaqu\'in Peralta},
\textbf{Claudia Loyola}, \textbf{Felipe Gonz\'alez} and \textbf{Sergio Davis},
the last one is the principal programmer. The work team aims that {\lpmd}
attract the attention of future programmers and colaborators in the project,
could be improving or developing plugins as well as suggestions and
recommendations about the program.

\begin{itemize}

\item \underline{\sc Principal Developers:} People that give the initial
kick in the project to generate the first versions of the {\lpmd} code. At this
moment everyone still be an active member of the {\lpmd} community and are
working in different areas providing a variety of aspects at the code,
prioritizing upgrades systems, efficient developing, friendly to the end--user,
support to the final user, documentation and web administration.

\begin{itemize}
 \item Sergio Davis, Royal Institute of Technology, 
 \href{http://www.lpmd.cl/sdavis/}{\tt sergdavis@gmail.com}.
 \item Claudia Loyola, Universidad de Chile, 
 \href{http://www.lpmd.cl/claudial/}{\tt claudial.81@gmail.com}.
 \item Joaqu\'in Peralta, Universidad de Chile, 
 \href{http://www.lpmd.cl/jperalta/}{\tt jperaltac@gmail.com}.
 \item Felipe Gonz\'alez, Universidad de Chile, 
  \href{http://www.gnm.cl/fgonzalez/}{\tt fullofmetal@gmail.com}.
\end{itemize}

\item \underline{\sc External Developers:} They gave to the project, and some
of them still doing,  support to the code, in areas like utilization,
control and studies. Even modifications and direct new developing tool. We hope
that soon more new interested developers want bring to us and with their help
improve the code and the utilities of {\lpmd}.

\begin{itemize}
 \item Yasm\'in Navarrete, Universidad de Chile, 
 {\tt yasmin.navarrete@gmail.com}.
 \item Pablo Ravelo, Universidad de Chile, 
 \href{http://www.gnm.cl/~pravelo/}{\tt pablo.ravelo@gmail.com}.
\end{itemize}

\item \underline{\sc Collaborators:} They are the principal motivators 
of the {\lpmd} project in order to still working with this project. And they
give us suggestions, corrections, contributions to the ideas and overview of
{\lpmd}. From technical details to physics are under every improvement.

\begin{itemize}
 \item PhD Gonz\'alo Guti\'errez
(\href{http://fisica.ciencias.uchile.cl/~gonzalo/}{\tt
gonzalo@fisica.ciencias.uchile.cl}).
 \item PhD Eduardo Men\'endez
(\href{http://fisica.ciencias.uchile.cl/~emenendez/}{\tt
emenendez@fisica.ciencias.uchile.cl}).
 \item PhD Carlos Esparza.
\end{itemize}
\end{itemize}

Any questions, contribution or suggestions, is always welcome in our little
community. Please do not hesitate to contact us, could be using e-mail to
any specific author or directly by the web page \href{http://www.lpmd.cl}{\tt
http://www.lpmd.cl} or e-mail address {\tt admin@lpmd.cl}.
